FictionEro - Affective Impact of Fiction

### 2025-08-08 analysis/analysis.qmd
attempt at making graph

dfsub1 <- dfsub <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/refs/heads/main/study1/data/data_participants.csv")
df1 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/refs/heads/main/study1/data/data.csv") |> 
  right_join(
    select(dfsub, Participant, Sample, Language, Mobile, starts_with("Feedback_"), 
           BAIT_Visual, BAIT_Text, AI_Knowledge, SexualActivity, 
           GAAIS_Negative, GAAIS_Positive, Porn, COPS_Frequency_2,
           Screen_Size,
           -Feedback_Comments),
    by = "Participant"
    ) |> 
  datawizard::rescale(select=c("Valence"), range=c(-1, 1), to=c(0, 1)) |> 
  mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
         Relevance =  fct_relevel(Relevance, "Relevant", "Irrelevant", "Non-erotic"),
         Sex =  fct_relevel(Sex, "Male", "Female"),
         PornFrequency = as.numeric(as.factor(COPS_Frequency_2)),
         SexualActivity_num = as.numeric(as.factor(SexualActivity)),
         ConditionBelief = case_when(
           Condition == "Photograph" & Realness > 0.5 ~ "True",
           Condition == "AI-Generated" & Realness < 0.5 ~ "True",
           .default = "False"
         )) |> 
  mutate(across(starts_with("Feedback_"), function(x) {fct_relevel(x, "False", "True")}))
```

@@

```{r}
arousal1 <- readRDS("models/ModelArousal_1.rds")
results_table(arousal1)

pred_a1 <- estimate_means(arousal1, by = c("Sex", "Relevance", "Condition", "ConditionBelief"), backend = "emmeans")  |>
  as.data.frame()

pred_a1|>
  mutate(Sex = fct_relevel(Sex, "Male", "Female")) |>
  ggplot(aes(x = Arousal, y= Proportion ))

```{r}
arousal2 <- readRDS("models/ModelArousal_2.rds")
results_table(arousal2)

pred_a2 <- estimate_means(arousal2, by = c("Gender","Condition", "ConditionBelief"), backend = "emmeans") |>
  as.data.frame()
```

>>>>

dfsub1 <- dfsub <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/refs/heads/main/study1/data/data_participants.csv")
df1 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/refs/heads/main/study1/data/data.csv") |> 
  right_join(
    select(dfsub1, Participant, Sample, Language, Mobile, starts_with("Feedback_"), 
           BAIT_Visual, BAIT_Text, AI_Knowledge, SexualActivity, 
           GAAIS_Negative, GAAIS_Positive, Porn, COPS_Frequency_2,
           Screen_Size,
           -Feedback_Comments),
    by = "Participant") |> 
  datawizard::rescale(select=c("Valence"), range=c(-1, 1), to=c(0, 1)) |> 
  mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
         Relevance =  fct_relevel(Relevance, "Relevant", "Irrelevant", "Non-erotic"),
         Sex =  fct_relevel(Sex, "Male", "Female"),
         PornFrequency = as.numeric(as.factor(COPS_Frequency_2)),
         SexualActivity_num = as.numeric(as.factor(SexualActivity)),
         ConditionBelief = case_when(
           Condition == "Photograph" & Realness > 0.5 ~ "True",
           Condition == "AI-Generated" & Realness < 0.5 ~ "True",
           .default = "False"
         )) |> 
  mutate(across(starts_with("Feedback_"), function(x) {fct_relevel(x, "False", "True")}))
```

@@

```{r}
arousal1 <- readRDS("models/ModelArousal_1.rds")
arousal2 <- readRDS("models/ModelArousal_2.rds")
```

pred_a <- rbind(
  modelbased::estimate_means(arousal1, by = c("Sex", "Relevance", "Condition", "ConditionBelief"), backend = "emmeans")  |>
    filter(Relevance == "Relevant") |>
    select(-Relevance) |>
    rename(Gender = "Sex") |>
    mutate(Sample = "Study 1")|>
  as.data.frame(), 
  modelbased::estimate_means(arousal2, by = c("Gender","Condition", "ConditionBelief"), backend = "emmeans")|>
    mutate(Sample = "Study 2") |>
    as.data.frame())

pred_a |>
  ggplot(aes(x = ConditionBelief,y = Proportion, color = Condition,linetype = Sample, group = interaction(Sample, Condition))) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = CI_low, ymax = CI_high),width = 0.1) +
  facet_wrap(~ Gender) +
  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal(base_size = 14) +
  theme(
        axis.text.y = element_text(size = 8),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 10),
        strip.text.y = element_text(size = 10),
        axis.text.x = element_text(face = "bold", size=9, color="black"),
        legend.text = element_text(size = 10),
        legend.position =  ) +
  labs(x = "Whether the original labels were believed to be true",y = "Estimated Proportion",color = "Images presented as:",linetype = "Sample")
```

### Enticement

```{r}
enticement1 <- readRDS("models/ModelEnticement_1.rds")
enticement2 <- readRDS("models/ModelEnticement_2.rds")
```

### Valence

```{r}
valence1 <- readRDS("models/ModelValence_1.rds")
valence2 <- readRDS("models/ModelValence_2.rds")
```
